\disstitle

### 2018-06-17 chapters/introduction/introduction.tex
introduction draft

Many research has been done to detect the camera
geometry from input images. \todo{citation and examples}. Most of the
previous work optimize for a limited set of camera calibration
parameters only. However, our research found that there exists an
effective way of optimizing multiple camera calibration parameters at
simultaneously (refer to \chapref{mcmc}). Our method use the Monte
Carlo Markov Chain (MCMC) method to sample the possible solutions that
minimize the objective function, which measures the ``matchness''
between the observation (input image) and the camera calibration.

@@

  \item \textbf{Camera Geometry for Image Understanding:}
  \todo{more writing}
  We explore the potentials of camera geometry for image understanding.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.

@@

  \item \textbf{\chapref{crosstransf} -
  Cross-view Domain Adaptation:} \newline \newline
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projection losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. \newline

>>>>

Many research has been done to detect the camera
geometry from input images. \todo{citation and examples}. Most of the
previous work optimize for a limited set of camera calibration
parameters only. However, our research found that there exists an
effective way of optimizing multiple camera calibration parameters at
simultaneously (refer to \chapref{mcmc}). Our algorithm uses the Monte
Carlo Markov Chain (MCMC) method to sample the possible solutions that
minimize the objective function, which measures the ``matchness''
between the observation (input image) and the camera calibration.

@@

  \item \textbf{Camera Geometry for Image Understanding:}
  We explore the potentials of camera geometry for image understanding.
  Current machine learning methods address problems that involves mostly
  the ground imagery. 
  Studies around overhead images are relatively less thus much fewer
  annotated data exists in public. With the camera geometric
  information, we can pair the ground imagery with overhead imagery to
  form cross-view pairs. Our algorithm explore how to transfer the
  learned knowledge from a network designed for ground level image
  semantic segmentation to a new network designed for overhead imagery
  semantic segmentation use these cross-view pairs.
  Furthermore, we also explore the potential of the camera geometry as
  weak annotation in supervised learning. Our algorithm shows that by
  directly learning to predict camera locations, the network networks
  are able to extract high-level geo-temporal features.

@@

  \item \textbf{\chapref{crosstransf} -
  Cross-view Domain Adaptation:} \newline \newline
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projective losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. \newline
